---
output: html_document
editor_options: 
  chunk_output_type: console
---




## Effect of Condition {.tabset}

### Confidence

- Significant interaction between the condition and the answer: the effect of answer (being more confident in truths than in lies) is lower in the interrogation condition.
- Effect mostly driven by lower lie confidence in the polygraph condition: less obvious feedback cues?

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-5, 5, length.out=100), dstudent_t(seq(-5, 5, length.out=100), 1, 0, 1), "l")

model <- brms::brm(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Condition", "Answer")) |> 
  plot(show_data = "none") 
```

### RT

- Significant main effect of the condition: people are slower in the polygraph condition.
- Consistent with the "less intuitive cues".

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")

model <- brms::brm(RT ~ Answer * Condition + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 3)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Condition", "Answer")) |> 
  plot(show_data = "none") 
```

### Heart Rate

- Higher heart rate in lies vs. truths.
- Higher heart rate in interrogation condition vs. polygraph: presence of another person causes heightened physiological arousals.
- No interaction.

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-30, 30, length.out=100), dstudent_t(seq(-30,30, length.out=100), 1, 0, 8), "l")
model <- brms::brm(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 8)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition")
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Condition", "Answer")) |> 
  plot(show_data = "none") 
```



## Effect of Phrasing {.tabset}

- Main effect of phrasing on RT only. Indirect questions lead to slower answers.

### Confidence

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-2, 2, length.out=100), dstudent_t(seq(-2, 2, length.out=100), 1, 0, 1), "l")

model <- brms::brm(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Answer", "Phrasing")) |> 
  plot(show_data = "none") 
```

### RT

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")

model <- brms::brm(RT ~ Answer * Phrasing + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 3)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Answer", "Phrasing")) |> 
  plot(show_data = "none") 
```



### Heart Rate

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-50, 50, length.out=100), dstudent_t(seq(-50, 50, length.out=100), 1, 0, 8), "l")
model <- brms::brm(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 8)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
estimate_means(model, at = c("Answer", "Phrasing")) |> 
  plot(show_data = "none") 
```

