---
title: '**The Role of Interoception and Theory of Mind in Deception**'
author: "Dominique Makowski et al."
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    toc: yes
    toc_depth: 3
    df_print: default
    code_folding: hide
    code_download: yes
editor_options:
  chunk_output_type: console
---


<!-- 
!!!! IMPORTANT: run `source("utils/render.R")` to publish instead of clicking on 'Knit'
-->

```{r setup, warning=FALSE, message=TRUE, include=FALSE}
# Set up the environment (or use local alternative `source("utils/config.R")`)
source("https://raw.githubusercontent.com/RealityBending/TemplateResults/main/utils/config.R")

options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr",
  dplyr.summarise.inform = FALSE
)

knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
theme_set(see::theme_modern())
```


```{r warning=FALSE, message=TRUE, results='asis'}
library(tidyverse)
library(patchwork)
library(glmmTMB)
library(brms)
library(easystats)

show_parameters <- function(model) {
  p <- parameters::parameters(model, effects = "fixed", component="conditional", test=c("pd")) |>
    data_relocate("pd", after=-1)
  display(p, stars=TRUE)
}
```

```{r warning=FALSE, message=TRUE, results='asis'}
summary(report::report(sessionInfo()))
```


```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(Participant = factor(paste0("S", Participant), levels = paste0("S", 1:30)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

# Outliers
df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
# df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
df$RT[df$Participant == "S13"] <- NA # Slower than the others


# Remove outlier trials
df <- df |>
  group_by(Participant) |>
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.99999))),
         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.99999)))) |>
  ungroup()

# Adjustments for beta models
df$Confidence[df$Confidence == 1] <- 0.99999
df$Confidence[df$Confidence == 0] <- 0.00001

cat(paste("The data consists of",
          report::report_participants(df,
                                      participants = "Participant",
                                      sex = "Gender",
                                      age = "Age")))
```

Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %


# Measures {.tabset}

```{r child='1_Measures.Rmd'}
```


# Dimension Reduction 

## Theory of Mind

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_")) |> 
  select(-ends_with("Total")) |> 
  group_by(Participant) |> 
  summarise_all(mean) |> 
  select(-Participant)

parameters::n_factors(dfsub)
efa <- parameters::factor_analysis(dfsub, n=1, sort=TRUE, rotation = "oblimin")
efa

df <- cbind(df, predict(efa, newdata=df, names="ToM"))
```


## Interoception

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("HCT_"), 
         starts_with("MAIA_")) |> 
  select(-ends_with("Total")) |> 
  group_by(Participant) |> 
  summarise_all(mean) |> 
  select(-Participant)

parameters::n_components(dfsub)
efa <- parameters::factor_analysis(dfsub, n=4, sort=TRUE, rotation = "oblimin")
efa
df <- cbind(df, predict(efa, newdata=df, names=c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")))
```


# Manipulation Checks

```{r child='2_ManipulationChecks.Rmd'}
```

# Theory of Mind / Empathy



## Theory of Mind Score {.tabset}


### Confidence

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("ToM")) {
  model <- brms::brm(as.formula(paste0("Confidence ~ Answer / (Condition / ",
                                     var,
                                     ") + (1|Participant) + (1|Item)")),
                   data = df, family = "beta", refresh=0, seed=3, iter=4000,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$ToM, stars = TRUE))
```

### RT


```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("ToM")) {
  model <- brms::brm(as.formula(paste0("RT ~ Answer / (Condition / ",
                                     var,
                                     ") + (1|Participant) + (1|Item)")),
                   data = df, refresh=0, seed=3, iter=4000,
                   prior = set_prior("student_t(1, 0, 3)", class = "b"))

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$ToM, stars = TRUE))
```


### Heart Rate

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("ToM")) {
  model <- brms::brm(as.formula(paste0("HeartRate ~ Answer / (Condition / ",
                                     var,
                                     ") + (1|Participant) + (1|Item)")),
                   data = df, refresh=0, seed=3, iter=4000,
                   prior = set_prior("student_t(1, 0, 8)", class = "b"))

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$ToM, stars = TRUE))
```




### Correlation with LIE Scale

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  select(Participant,
         starts_with("LIE_"),
         starts_with("ToM")) |>
  group_by(Participant) |>
  summarise_all(mean)

correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("ToM")), bayesian=TRUE)
```




```{r child='3_ToM.Rmd'}
```

# Interoception


## Interoception Scores {.tabset}


### Confidence

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
  model <- brms::brm(as.formula(paste0(
    "Confidence ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, family = "beta", refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 1)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$Intero_Meta, stars = TRUE))
display(format_table(results$Intero_Listening, stars = TRUE))
display(format_table(results$Intero_Focus, stars = TRUE))
display(format_table(results$Intero_Regulation, stars = TRUE))
```


### RT


```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
  model <- brms::brm(as.formula(paste0(
    "RT ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 3)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$Intero_Meta, stars = TRUE))
display(format_table(results$Intero_Listening, stars = TRUE))
display(format_table(results$Intero_Focus, stars = TRUE))
display(format_table(results$Intero_Regulation, stars = TRUE))
```


### Heart Rate

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("Intero_Meta", "Intero_Listening", "Intero_Focus", "Intero_Regulation")) {
  model <- brms::brm(as.formula(paste0(
    "HeartRate ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 8)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$Intero_Meta, stars = TRUE))
display(format_table(results$Intero_Listening, stars = TRUE))
display(format_table(results$Intero_Focus, stars = TRUE))
display(format_table(results$Intero_Regulation, stars = TRUE))
```




### Correlation with LIE Scale

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  select(
    Participant,
    starts_with("LIE_"),
    starts_with("Intero_")
  ) |>
  group_by(Participant) |>
  summarise_all(mean)

correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("Intero_")), bayesian = TRUE)
```




```{r child='4_Intero.Rmd'}
```



# Deception Trait {.tabset}

## Confidence

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "Confidence ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, family = "beta", refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 1)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```


## RT


```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "RT ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 3)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```


## Heart Rate

```{r message=FALSE, warning=FALSE}
results <- list()
for (var in c("LIE_Ability", "LIE_Frequency", "LIE_Contextuality", "LIE_Negativity")) {
  model <- brms::brm(as.formula(paste0(
    "HeartRate ~ Answer / (Condition / ",
    var,
    ") + (1|Participant) + (1|Item)"
  )),
  data = df, refresh = 0, seed=3, iter = 4000,
  prior = set_prior("student_t(1, 0, 8)", class = "b")
  )

  results[[var]] <- parameters::parameters(model, effects = "fixed", component = "conditional", test = c("pd"), keep = var) |>
      as.data.frame() |> 
      separate(Parameter, sep = ":", into = c("Answer", "Condition", "Variable")) |>
      mutate(
        Answer = str_remove(Answer, "b_Answer"),
        Condition = str_remove(Condition, "Condition")
      )
}

display(format_table(results$LIE_Ability, stars = TRUE))
display(format_table(results$LIE_Frequency, stars = TRUE))
display(format_table(results$LIE_Contextuality, stars = TRUE))
display(format_table(results$LIE_Negativity, stars = TRUE))
```



# Figure

```{r warning=FALSE, message=FALSE, eval=FALSE}
data <- df |>
  group_by(Participant, Answer, Condition) |> 
  select(Confidence, RT, HeartRate, ToM, Intero_Regulation, Intero_Focus, Intero_Meta, Intero_Listening) |> 
  summarise_all(.funs = list(Mean = function(x) mean(x, na.rm = TRUE), 
                             low = function(x) (mean(x, na.rm=TRUE) - sd(x, na.rm=TRUE) / 2),
                             high = function(x) (mean(x, na.rm=TRUE) + sd(x, na.rm=TRUE) / 2))) |> 
  mutate(ToM_Mean = ifelse(Condition == "Polygraph", ToM_Mean-0.01, ToM_Mean+0.01),
         Intero_Regulation_Mean = ifelse(Condition == "Polygraph", Intero_Regulation_Mean-0.01, Intero_Regulation_Mean+0.01),
         Intero_Focus_Mean = ifelse(Condition == "Polygraph", Intero_Focus_Mean-0.01, Intero_Focus_Mean+0.01),
         Intero_Meta_Mean = ifelse(Condition == "Polygraph", Intero_Meta_Mean-0.01, Intero_Meta_Mean+0.01),
         Intero_Listening_Mean = ifelse(Condition == "Polygraph", Intero_Listening_Mean-0.01, Intero_Listening_Mean+0.01))

model <- glmmTMB(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
                 data = df, 
                 family = beta_family())

model <- brms::brm(Confidence ~ Answer / Condition / ToM + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

link_data <- estimate_relation(model, at = c("Condition", "Answer", "ToM"), length = 30)

p1 <- ggplot(link_data, aes(x = ToM, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = ToM_Mean,
                      xend = ToM_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = ToM_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(ToM = -0.3, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = "Theory of Mind") +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p1
  

model <- brms::brm(Confidence ~ Answer / Condition / Intero_Meta + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Meta"), length = 30)

p2 <- ggplot(link_data, aes(x = Intero_Meta, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Meta_Mean,
                      xend = Intero_Meta_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Meta_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Meta = -0.15, Predicted = 0.25, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p2



model <- brms::brm(Confidence ~ Answer / Condition / Intero_Listening + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Listening"), length = 30)

p3 <- ggplot(link_data, aes(x = Intero_Listening, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Listening_Mean,
                      xend = Intero_Listening_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Listening_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white")) 
  
p3


model <- brms::brm(Confidence ~ Answer / Condition / Intero_Focus + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))
link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Focus"), length = 30)

p4 <- ggplot(link_data, aes(x = Intero_Focus, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Focus_Mean,
                      xend = Intero_Focus_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Focus_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Focus = -0.2,
                            Predicted = c(0.55, 0.75),
                            Condition = c("Polygraph", "Interrogation"),
                            Answer = c("Truth", "Truth")),
            label = c("*", "*"),
            color = c("#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p4



model <- brms::brm(Confidence ~ Answer / Condition / Intero_Regulation + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

link_data <- estimate_relation(model, at = c("Condition", "Answer", "Intero_Regulation"), length = 30)

p5 <- ggplot(link_data, aes(x = Intero_Regulation, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Regulation_Mean,
                      xend = Intero_Regulation_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Regulation_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Regulation = -0.15, 
                            Predicted = c(0.25, 0.45, 0.75),
                            Condition = c("Polygraph", "Interrogation", "Polygraph"), 
                            Answer = c("Lie", "Lie", "Truth")),
            label = c("***", "*", "*"),
            color = c("#FF5722", "#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white")) 
p5


p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing lie", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
p
ggsave("figures/Figure1.png", width=12, height=15)
```


# References

```{r warning=FALSE, message=FALSE, results='asis'}
report::cite_packages(sessionInfo())
```


