---
title: '**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
shorttitle        : "TITLE"
author:
  - name          : "Dominique Makowski"
    affiliation   : " 1, *"
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dmakowski@ntu.edu.sg"
  - name          : "Zen J. Lau"
    affiliation   : " 1"
  - name          : "Tam Pham"
    affiliation   : " 1"
  - name          : "S.H. Annabel Chen"
    affiliation   : " 1, 2, 3, 4"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-19, 48 Nanyang Avenue, Singapore"
    email         : "annabelchen@ntu.edu.sg"
affiliation:
  - id            : "1"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "2"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Nanyang Technological University, Singapore"
abstract: |
output:
  papaja::apa6_word:
    keep_tex: yes
  pdf_document: default
  papaja::apa6_pdf:
    keep_tex: yes
keywords: ""
wordcount: ''
bibliography: ["references.bib"]
floatsintext: yes
figsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
header-includes:
- \usepackage[labelfont=bf, font={color=gray,small}]{caption}
- \usepackage{float}
- \usepackage[document]{ragged2e}
csl: utils/apa.csl
---

\justify

```{r r_setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library("kableExtra")
options(knitr.kable.NA = 'None')
```

```{=html}
<!-- 
Journals:
Neuroscience Letters https://www.journals.elsevier.com/neuroscience-letters
Biological Psychology https://www.journals.elsevier.com/biological-psychology
Psychophysiology https://onlinelibrary.wiley.com/journal/14698986
Cognitive Neurodynamics https://www.springer.com/journal/11571
Neuroscience & Biobehavioral Reviews https://www.journals.elsevier.com/neuroscience-and-biobehavioral-reviews
-->
```
# Introduction

<!-- Little intro-->

In this post-truth era, deception has become increasingly prevalent in our everyday lives [@lewandowsky2017beyond]. Although the act of deceiving is regarded as complex and often requires effortful self-regulation to conceal [@abe2007deceiving; @krokoszinski2016emotion], research shows that people tend to under-estimate their ability to successfully lie [@elaad2003effects]. However, relative to the abundant literature regarding deception detection [@viji2022history; @sternglanz2019review; @masip2017deception], surprisingly little attention has been conferred to investigating the inter-individual differences in people's ability to lie. Given meta-analytic findings wherein the deceptive ability of the liar is suggested to be more important than the lie detector in deceptive interactions [@verigin2019lie; @bond2008individual; @levine2011sender], it is perhaps more pertinent to investigate what makes someone a better liar.

<!-- TOM  -->

As deception requires the liar to intentionally manipulate the beliefs of others [@burgoon1994interpersonal; @sip2012if], most research on lying capability has been focused on higher order cognitive processes, particularly in theory of mind (TOM). TOM refers to the ability to infer that others have mental states, such as beliefs, emotions and intentions, distinct from ourselves [@lee2021lying; @wellman2001meta; @baron1997mindblindness]. Indeed, the capacity to tell lies, as well as the complexity of lies told, have previously been found to be related to higher TOM abilities [@talwar2007lying; @evans2011verbal; @talwar2017role]. Furthermore, the deceptive capabilities of children is often used as a measure of their TOM abilities. However, studies investigating the links between TOM and lying ability have predominantly been focused on children and individuals with neurocognitive deficits [@beaudoin2020systematic; @bora2017meta; @roheger2022progression]; likely a result of the view of TOM as the foundation of other higher order cognitive processes [@ketelaars2010dynamics; @isaksson2021s]. As such, little is known regarding the role TOM plays in the lying ability of healthy adults.   


<!-- Intero in Deception research -->

Alternatively, differences in interoception could also be a factor worthy of consideration. Broadly defined as one's sensitivity to their own internal signals and bodily states [@murphy2019classifying; @chen2021emerging; @weiss2014interaction], interoception has increasingly been tied to subjective perceptual experiences [@connell2018interoception; @seth2012interoceptive], as well as individual differences in executive functions, emotional processing and decision-making [@barrett2015interoceptive; @petzschner2021computational; @murphy2019classifying].

Given the established link between interoceptive abilities and emotional processing [@barrett2015interoceptive; @petzschner2021computational; @vabba2022interoceptive], it is possible that interoception bears influence on people's capacity to tell lies. Although there has been little research investigating the relationship between interoception and deceptive ability *per se*, some studies have found heightened self-focus towards internal bodily signals to be associated with an increased demonstration of apathetic, immoral behaviour, such as cheating [@ditto2006visceral; @williams2016valjean; @lenggenhager2013listening]. In line with these findings, @vabba2022interoceptive further reports individuals with lower interoception told significantly less egoistic lies when the social reputational stakes were high (relative to low), whereas individuals with higher interoception did not exhibit a significant difference in the number of lies told. 

In contrast, previous decision-making studies have shown a negative correlation between interoceptive awareness and one's likelihood of making risky decisions [@dunn2010listening; @furman2013interoceptive]. In fact, this is consistent with the somatic marker hypothesis, which posits interoception to be associated with a propensity towards making rational decisions [@damasio1996somatic]. While the literature pertaining to interoception seems contradictory, it is possible that these mixed findings are a result of a failure to take into consideration interoception's multidimensionality. According to @garfinkel2015knowing's three-dimensional framework, interoception is comprised of three distinct facets, namely - *interoceptive accuracy*, the objective ability to monitor internal bodily signals; *interoceptive sensibility*, the subjective confidence in one's interoceptive accuracy; and *interoceptive awareness*, the metacognitive awareness of one's interoceptive accuracy (i.e., accuracy-confidence correspondence). However, previous interoception research has largely been focused on interoceptive accuracy [@wallman2021physical]. Taking this to perspective with the paucity in studies linking deceptive ability with interoception, more studies are warranted to comprehensively examine the relationship between interoception and deception.      

<!-- Interoceptive processes are not only a key component of forming your own emotions, but may also facilitate being in tune with the emotional states of others [@konvalinka2011synchronized; @garfinkel2016discrepancies]. This corresponds to situations involving deception, since much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered]. While research indicates that attending to ones interoceptive cues improves success in unmasking detection [@ten2019different], there is limited information how interoceptive skills may function the other way around, in the case of the liar. -->

<!-- As identified by @murphy2022propensity, the propensity to use interoceptive information, and in what manner remains an underdeveloped area in research, and may illuminate the mechanisms underlying physiological and emotional control exhibited by successful liars [@krokoszinski2016emotion; @wielgopolan2021can]. -->

<!-- Hypothesis -->

The aim of the present study was to explore the interplay effects of TOM and interoception on individuals' deceptive ability, as indicated by their lie confidence, physiological arousal and response time. To this end, we designed a directed-lying bi-modal feedback paradigm comprising 2 conditions ( *Interrogation* vs *Polygraph*) with distinct feedback cues. In particular, salient social feedback cues were conferred during the *Interrogation condition*, whereas physiological feedback cues were given during the *Polygraph condition*. We expected interoception to positively predict lying ability in the *Polygraph condition*, and have no significant effect on one's ability to lie in the *Interrogation condition*. Similarly, we hypothesized that TOM would positively predict individuals' capability in lying in the *Interrogation condition* and exhibit non-significant effects in the *Polygraph condition*.  


# Methods

Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){uri.}.


## Participants

30 participants were recruited through  posters, flyers, and online social media platforms. Inclusion criteria included residing in Singapore, and an absence of current or history of neurological, psychiatric, or cardiovascular disorders. 4 participants were excluded as a result of a technical error that led to their data not being recorded. The final sample consists 26 participants (Mean age = 20.9, SD = 2.0, range:[18, 25], Sex: 65.4% women, 34.6% men, 0.00% non-binary). The heart rate of one participant and response time of one participant were excluded from further analysis due to extreme outlying values [**PLEASE HELP ME CONFIRM**]. 

This study was approved by the NTU Institutional Review Board (NTU IRB-2018-10-029)(**TBC**) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration. All participants provided their informed consent prior to participation and were awarded with academic credit upon completion of the study. 

 

## Measures

### Theory of Mind

The *Basic Empathy Scale (BES)* is a 20-item, 5-point Likert scale (Strongly Disagree - Strongly Agree) that measures cognitive and affective empathy [@jolliffe2006development]. Although TOM and empathy are regarded as distinct psychological constructs, previous research findings point to them being closely related [@gallant2020developing; @sebastian2012neural]. Specifically, empathy is often thought to be an integral component in the affective dimension of TOM (i.e., the ability to infer what someone else is feeling) [@shamay2010role]. The *Yoni Task*, which comprises 3 dimensions, namely cognitive, physical and affective, was also administered to assess participants' objective TOM ability [@shamay2007dissociable].

### Interoceptive Abilities

To assess particpants' interoceptive ability, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart] while having their actual heartbeats recorded. During the HCT task, participants were instructed to count the number of heartbeats they felt over 5 trials with varying time intervals (20s, 25s, 30s, 35s, 40s), the sequence of which was randomized. Interoceptive accuracy (*HCT Accuracy*) was then computed based on the absolute difference between the actual number of heartbeats and the number of heartbeats counted during each trial. To assess their interoceptive sensibility (*HCT Confidence*), participants were asked to indicate, on a visual analog, how confident they were of their heartbeat counting accuracy at the end of each trial. 

The *MAIA-2* [@mehling2012multidimensional], a 32-item questionnaire which measures 8 dimensions of interoception (Noticing, Not-Distracting, Not-Worrying, Attention, Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust) using a 5-point Likert scale (Never-Always) was also administered.

### Lie Profile

To evaluate participants' tendency to lie in their everyday lives, we used the *LIE Scale*, a 16-item questionnaire that assesses 4 dispositional lying dimensions (Ability, Negativity, Contextuality and Frequency) on a visual analog scale (Disagree-Agree) [@makowski2021structure].

### Demographic Information

We further collected demographic information including age, ethnicity, nationality, handedness (for application of EDA electrodes), religion, duration lived in Singapore as well as highest education qualification achieved (or in the midst of achieving). 

### Deception Task Paradigm

We designed a computerized directed-lying experimental paradigm (the *Deception Task*) consisting of 2 conditions (the *Interrogation Condition* and the *Polygraph Condition*) to assess participants' lying ability. 

In the **Interrogation Condition**, participants' response to each trial was followed by social feedback in the form of a video stream with an examiner. Notably, participants were informed that the examiner would be evaluating the truthfulness of their responses by observing them through the live video feed. In actuality, the video was a pre-recorded video clip of a confederate, and the same video-clip was presented to all participants.

In the *Polygraph condition*, participants' response to each trial was followed by physiological feedback in the form of an electrocardiogram (ECG) instead. Specifically, participants were informed that they were being shown live feedback of their own physiological signals when in fact, the displayed ECG was that of a pre-recorded video clip. Similar to the *Interrogation Condition*, all participants were shown the same pre-recorded video clip of an electrocardiogram. 

Regardless of the task condition, participants were presented with a question, either phrased directly (*"What is your favourite sport?*), or indirectly (*"Is your favourite sport Hockey?"*), on a computer screen with accompanying instructions that either asked participants to verbally lie or tell the truth following each *Deception Task* trial. These instructions were displayed for a maximum of 10 seconds, or until the participants responded. Following each response, participants were then asked to rate their confidence in how convincing their answer was, before progressing to the next trial.

## Procedure

In the first phase of the study, participants answered a brief demographic survey before being administered a battery of questionnaires (*BES*, *MAIA-2*, *Lie Scale*) and cognitive-behavioural tasks (*HCT*, *Yoni Task*). This series of tasks and questionnaires were administered in a randomized order [**TBC**] in order to control for order effects. In the second phase of the study, the *Deception Task* paradigm was presented to participants. Similar to the first phase, the order sequence of the 2 conditions (*polygraph* vs *interrogation*) was randomized [**TBC**], with each condition comprising 40 trials. Within each condition, participants were instructed to lie in half of the trials (20 truth trials; 20 lie trials). In total, each participant underwent 80 *Deception Task* trials, of which they had to respond with either lies or truths depending on the given instruction.

Physiological recording devices were prepared prior to beginning the experimental paradigm. Using three ECG electrodes placed according to a modified Lead II configuration [@takuma1995alternative], cardiovascular activity, sampled at 1000Hz (**TBC**) was recorded via the BioPac MP160 system (BioPac Systems Inc., USA) and the AcqKnowledge 5.0 software. Events were marked by a photosensor attached to the screen.  

## Data Analysis

The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs. indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' confidence ratings that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response. This analysis was performed using mixed models with the participants and questions both entered as random factors. Marginal contrasts analysis was also performed to clarify the differences between conditions. To allow for a better quantification of the uncertainty associated with the effects, as well as increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [@makowski2019bayestestr], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).

To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, TOM and interoception). We favoured the use of factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, @parametersArticle), over PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained. Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation). Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.

The data analysis was carried out using*R 4.2* [@RCoreTeam2022], *brms* [@Burkner2017], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle]. As the full reproducible analysis script and statistical results are available at [**https://github.com/DominiqueMakowski/DeceptionInteroTom**](https://github.com/DominiqueMakowski/DeceptionInteroTom){.uri}, we will only focus on significant results in the manuscript.

# Results

## Manipulation Check

Compared to truth, lies were rated with less confidence ($\beta=-1.09,~95\%~CI~[-0.94, -1.25],~pd = 100\%$). Moreover, lies told in the polygraph condition were rated with less confidence ($\delta=-0.24,~95\%~CI~[-0.10, -0.39],~pd > 99\%$). The RT did not differ between truth and lies, but was significantly slower in the polygraph condition ($\beta=0.14,~95\%~CI~[0.03, 0.25],~pd > 99\%$) for both conditions. The heart rate was significantly more elevated during lies as compared to truth ($\beta=1.31,~95\%~CI~[2.14, 0.50],~pd > 99.9\%$), and during interrogation as compared to the polygraph condition ($\beta=4.99 ,~95\%~CI~[5.82, 4.19],~pd = 100\%$).

The indirect phrasing of the question only had a significant effect on RT ($\beta=0.34,~95\%~CI~[0.23, 0.44],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.

## Feature Reduction

The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *TOM* (explaining 35.76% of variance). It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.

The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance). The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and Noticing (.49) dimensions of the MAIA and the HCT confidence score (.40). The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the Body Listening (.92) and Trusting (.53) MAIA dimensions, and the Awareness (-.60) and Confidence (.46) HCT scores. The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA Not-Distracting (.87), Emotional Awareness (-.40) and HCT Accuracy (.33). The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT Accuracy (.61) and MAIA Trusting (.40). However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.

## Theory of Mind

The composite *TOM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition. No significant effect was found with regards to heart rate, and no correlation was observed with dispositional lying traits.

## Interoception

The *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$). It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10%\%$), specifically in the polygraph condition. No significant association was found with heart rate.

The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$). It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition. No significant association was found with heart rate. This score also correlated with the dispositional lying *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).

The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$). No significant association was found with RT or heart rate, but the score correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).

The *Regulation* interoception score was significantly associated with an increased confidence in lies in the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$). No significant association was found with RT or heart rate.

# Discussion

While there is extensive literature associating deception with social cognition and emotion regulation, most of such research had been focused on deception detection, leaving a paucity in the studies pertaining to lying ability. This study hence seeks to address this research gap, further aiming to examine the interplay effect of TOM and interoception on deceptive ability. Using a bi-modal feedback deception task paradigm, participants were found to report significantly lower lie confidence in the *Polygraph condition*, relative to the *Interrogation condiiton*. Notably, we also found a significant association between several facets of interoception with individuals' lie confidence and response time in the polygraph condition. Taken together, this could be suggestive of people's greater reliance on social feedback cues when telling lies 


<!-- Participants relied on interoception -->

Our results show that participants who were telling the truth had a slower reaction time, and rated themselves as less confident in the polygraph condition, however, their heart rate averaged lower as compared to the interrogation condition. This suggests that despite the participant's lack of confidence, they were very in-tune with their physiological response in the polygraph condition, and successfully able to decrease their heart rate. Given that interoceptive accuracy is enhanced by focusing on it during a time of stress [@schulz2013cold], such as attempting to conceal deception combined with false physiological feedback delivered during the polygraph condition, this conclusion is in line with our hypothesis.

As the relationship between interoception and emotion is well established [@barrett2015interoceptive; @dobrushina2020interaction; @ohira2020predictive], our work is consistent with @wielgopolan2021can, who found that groups with higher emotional awareness made better liars and were more successful at regulating their emotional and physiological responses, as well as fabricating new ones.

<!-- Metacognition and Interoception -->

Although participants were not explicitly directed to attend to their physiological signals as a means of evading deception detection, they were aware these signals were recorded and informed that their lies would be detected through their analysis. Additionally, the presence of the ECG likely made them aware, and these measures remained connected during the interrogation. This indicates that there was likely an explicit attentional component to the control exerted, which is further reflected by a broader theme in our results. Our results indicate that all interoceptive factors (*Meta, Listening, Focus and Regulation*) are associated with an increased confidence in deceptive abilities, and faster reaction time for lies in the polygraph condition. It logical that confidence in deception would be accompanied by faster reaction time. However, since confidence was a subjective measure, it does not necessarily reflect competence [@khalsa2008interoceptive]. While our data indicates that participants were able to self-regulate using interoceptive abilities, this still highlights an important caveat, which is the potential metacognitive awareness at play [@garfinkel2015knowing].

Metacognitive beliefs, or interoceptive awareness about competence in the quality of physiological regulation may influence the cognitive processes and development physiological responses. That is to say, that the appraisal is just as important to the process of deception by informing their true ability [@stephan2016allostatic; @harrison2021filter; @petzschner2021computational].

<!-- Interoceptive sensibility and risk-taking -->

High interoceptive sensibility regardless of true competence may also directly shape behaviour through the reduced perception of risk associated with being caught. Past research indicates the likelihood of deception increases when individuals judge a lower risk of being caught, based on situation-specific variables and their own qualities [@sip2012if; @sip2013pinocchio]. These results may offer support to findings such as @vabba2022interoceptive where interoceptive abilities were found to be a significant moderator in the willingness to engage in riskier forms of deception, and offer insight into other risk behaviours linked with interoceptive ability such as cheating [@williams2016valjean] and risk-taking [@ditto2006visceral; @lenggenhager2013listening].

<!-- Future Research -->

While this research has demonstrated that interoceptive abilities may be used to regulate and conceal deception, the individual's confidence in their lying abilities, is subjective, and may not offer a full-picture of their objective success. Future research should continue to unpack this relationship, examining how confidence and interoceptive regulation is reflected in the actual success of a lie, as well as how individuals confidence in their interoceptive abilities may correspond to decision bias [@garfinkel2015knowing], and propensity to engage in deception [@sip2012if]. Furthermore, future research should expand recent findings on how individual traits correlate with true interoceptive abilities [@pearson2022two], to understand how they may factor into deceptive behaviour.

# Funding

# Author Contributions

# Conflict of Interest Statement

# Acknowledgements

\newpage

# References

```{r create_r-references}
r_refs(file = "references.bib")
```

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs}
:::

```{=tex}
\endgroup
```
