---
title: '**The Heart Lies: The Role of Interoception and Theory of Mind in Deception**'
shorttitle        : "TITLE"
author:
  - name          : "Dominique Makowski"
    affiliation   : " 1, *"
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dmakowski@ntu.edu.sg"
  - name          : "Zen J. Lau"
    affiliation   : " 1"
  - name          : "Tam Pham"
    affiliation   : " 1"
  - name          : "S.H. Annabel Chen"
    affiliation   : " 1, 2, 3, 4"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-19, 48 Nanyang Avenue, Singapore"
    email         : "annabelchen@ntu.edu.sg"
affiliation:
  - id            : "1"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "2"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "Lee Kong Chian School of Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Nanyang Technological University, Singapore"
abstract: |
output:
  papaja::apa6_word:
    keep_tex: yes
  pdf_document: default
  papaja::apa6_pdf:
    keep_tex: yes
keywords: ""
wordcount: ''
bibliography: ["references.bib"]
floatsintext: yes
figsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
header-includes:
- \usepackage[labelfont=bf, font={color=gray,small}]{caption}
- \usepackage{float}
- \usepackage[document]{ragged2e}
csl: utils/apa.csl
---

\justify

```{r r_setup, include = FALSE, warning=FALSE, message=FALSE}
library("papaja")
library("kableExtra")
options(knitr.kable.NA = 'None')
```

```{=html}
<!-- 
Journals:
Neuroscience Letters https://www.journals.elsevier.com/neuroscience-letters
Biological Psychology https://www.journals.elsevier.com/biological-psychology
Psychophysiology https://onlinelibrary.wiley.com/journal/14698986
Cognitive Neurodynamics https://www.springer.com/journal/11571
Neuroscience & Biobehavioral Reviews https://www.journals.elsevier.com/neuroscience-and-biobehavioral-reviews
-->
```
# Introduction

<!-- Little intro-->

The fabrication and delivery of false information is a sophisticated, and cognitively taxing activity [@abe2007deceiving; @leal2008time ], resulting in physiological arousal [@eskritt2021did] which may require effortful self-regulation to conceal[@krokoszinski2016emotion].

interoceptive deception detection etc

**EXPAND**

<!-- ToM-->

Much of the current research investigating the process and mechanisms involved in lying has considered capabilities such as Theory of Mind (ToM), the ability to understand and make inferences about other people's mental states and predict their behaviours [@el2017deception; @lee2021lying]. ToM is a critical component of deception, since the liar in question must be able to use their inferences to predict whether their target has accepted as true the false information presented to them [@stewart2019deception]. Children begin using deception during the same period of development in which executive function and ToM develops [@sai2021theory], and youth who have been trained in ToM saw an increase in lying behaviour [@ding2015theory]. However, there is a growing link between other cognitive and physiological mechanisms that may play a role in both deception detection, and fabricating successful lies

<!-- Define Intero and connect to deception -->

**Interoceptive sensibility? \< check if should use this term**

Interoceptive ability (IA) refers to a cluster of skills involved in monitoring, interpreting, integrating, and regulating one's visceral states[@chen2021emerging; @garfinkel2015knowing; @weiss2014interaction], and is closely tied to emotional and cognitive processes [@barrett2015interoceptive]. Much of the existing literature examining the link between interoceptive abilities has focused on how it may implicitly flag that one is being lied to through an elevated cardiac response [@gunderson2021body], and skin temperature [@van2014registered], or play a role in increasing body ownership. While research indicates that attending to ones interoceptive cues improves success in unmasking detection[@ten2019different], there is limited information how IA function the other way around, in the case of the liar.

<!-- Define Intero and and moral behaviour -->

Attending to interoceptive cues has been associated with greater willingness to engage in cheating [@williams2016valjean], risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening], and deception [@scattolin2021morality]. The work by @vabba2022interoceptive indicates that higher cardiac interoception is positively associated with the tendency to be dishonest, and tell higher egoistic lies. While this phenomena has been attributed to an increased sense of bodily ownership which accompanies focused awareness of one's viscera, other factors at play have also yet to be examined.

Given that the success of a lie depends more on the qualities of the deceiver versus the lie-detector [@verigin2019lie], fully understanding the link between IA and deception and other risk taking behaviours

It has been well established that some individuals, such as mindfulness practitioners with particularly high IA may be more confident in down-regulation of stress and associated physiological responses [@ardi2021effects; @fustos2013embodiment; @mcmahon2021mindful]. Since many of these cues, such as cardiac arousal and skin conductance are socially recognized as 'tells' that one is lying, and are used as primary indicators during the polygraph test, could those who are better at managing such responses lie more confidently?

<!-- Intero/and/or/metacognition -->

<!-- Hypothesis -->

The act of lying is often accompanied by physiological responses such as increased heart rate, increased respiration and sweating. Since fluctuations in key physiological indicators as a means to determine whether the individual is lying is a key principle behind the polygraph test and other lie detection techniques, there is a need for more research examining the relationship between IA, theory of mind, and deception. This research attempts to isolate the effects of theory of mind and interoception, and examine how they interact with deception. Of particular interest is how liars might utilize their interoceptive ability to self regulate in towards a more successful deception, and how this ability may compare or interact with other mechanisms at play such as theory of mind. We hypothesize that participants with greater theory of mind ability will show higher lie confidence, shorter reaction time, and lower physiological arousal in the interrogation condition, while participants in the polygraph condition will demonstrate lower lie confidence, lower reaction time and higher physiological arousal.

# Methods

Along with open science standards, the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) for this research is available at: **[LINK].**

The plan for this study was preregistered **(OSF?)**.

## Participants

*26* participants (65.4% Females, M~*age*~ = 20.9, *SD* = 2.0) were recruited advertising using univerisy mailing lists and posters. Participants were awarded with academic credit for their participation. This research was approved by the **Institutional Review Board (Reference Number: IRB-)** of Nanyang Technological University (NTU).

## Measures

### Theory of Mind and Empathy

Since Theory of Mind and empathy are closely related, *The Basic Empathy Scale (BES)* [@jolliffe2006development] was used as a subjective measure for theory of mind. *BES* uses a 40-item Likert scale to rate statements such as, "I can usually work out when people are cheerful" from 1-5. We also implemented the *Yoni Task,* which assesses the ability to judge mental states based on verbal cues, eye gaze and facial expression [@shamay2007dissociable].

### Interoceptive Ability

To measure interoception, participants completed a *Heartbeat Counting Task (HCT)* [@schandry1981heart], where participants count their heart beats without taking their pulse, as well as provide a confidence rating for their estimate. At the same time their true heart rate is recorded and the scores are compared to determine the individual's accuracy. They also completed the *MAIA questionnaire* [@mehling2012multidimensional], where they rated 32 statements such as "I can use my breath to reduce tension" on a 1-5 Likert scale.

Additionally, we implemented the Heartbeat Tracking Task (HTT) this is where they tap - **but not mentioned in the results??**

### Deception

We used the *LIE Scale*, which is a 44-item questionnaire examining deception as a dispositional trait, and measures the participant propensity towards lie frequency, ability, contextuality and negativity [@makowski2021structure].

### Demographic Information

The demographic information we collected was age, ethnicity, nationality, dominant hand (for application of EDA electrodes), education level (determined by highest qualification received, or in the midst of achieving), religion and duration lived in Singapore.

## Procedure

Each subject was briefed on the experimental procedure and study aims, and signed an informed consent document prior to the study commencing. During the first phase of the experiment, demographic measures were taken, followed by measures of Theory of Mind and interoceptive abilities, as described above. Participants were then connected to an electrocardiogram before proceeding with the deception task.

#### Deception Task

During the task, participants underwent 40 trails of a directed lying task (20 per condition), where they were asked questions such as, "What secondary school did you go to?". Participants provided their answer verbally and pressed a button when they were finished, at which point they would be connected for 10 seconds to the condition-unique stimulus.

In the Interrogation condition, participants were instructed that following their lie, a live examiner over video feed would appear briefly to judge whether they were truthful or not. In actuality, the video of the examiner shown was pre-recorded and the same for all participants. We hypothesized that participants would will rely on theory of mind abilities to predict whether their lie to the examiner was successfully accepted as true.

The Polygraph Condition followed the same routine, however instead of a receiving feedback from an interrogator, following the lie, a video of physiological signals was shown. We hypothesized when made acutely aware of such signals through false feedback, that participants would rely on interoceptive abilities to be more mindful or intentional about modulating the signals that may give them away. The physiological signals in this condition are also false feedback, and pre-recorded and identical for all participants.

During each trial, the time it took for participants to answer is recorded, and their heart rates are measured using an electrocardiogram. Following the trial, participants gave a confidence rating for how successful they believe their lie or truth was.

Debriefing was provided following the study. At this time the truthful answers to the directed lie questions were collected via questionnaire.

## Data Analysis

The manipulation checks consist of testing whether there is an effect of question phrasing (direct vs. indirect), and condition (polygraph *vs.* interrogation), on our 3 outcome variables: the participants' ratings of confidence that their answers (lies *vs.* truths) were convincing, the response time (RT), and the heart rate change associated with the response. This analysis was performed using mixed models with the participants and questions both entered as random factors. Marginal contrasts analysis was also performed to clarify the differences between conditions. To allow for a better quantification of the uncertainty associated with the effects, as well increase the robustness to outliers and artifactual findings, all statistics were undertaken under the Bayesian framework [**ref makowski2019existence**], using informative priors centred around 0 ($t_{Confidence}(1, 0, 1)$, $t_{RT}(1, 0, 3)$, $t_{Heartrate}(1, 0, 8)$).

To further counterbalance the low number of participants and maximize the signal-to-noise ratio, we performed a feature reduction on our two groups of predictor variables (namely, theory of mind and interoception). We used factor analysis (using the method agreement procedure to estimate the optimal number of dimensions, **REF PARAMETERS PKG**), rather PCA, as the goal was to extract meaningful and consistent factors, rather than merely maximizing the variance explained. Then, we modeled the relationship between these inter-individual composite scores (the analysis for all the variables is included in Supplementary Materials) and the 3 outcome variables in interaction with the condition (polygraph *vs.* interrogation). Finally, we also investigated the relationship between the deception scale traits, and the theory of mind and interoception scores using Bayesian correlations.

The data analysis was carried out using R, the *brms* package [*REF*] and the *easystats* ecosystem **[REFS]**. As the full reproducible analysis script and statistical results are available at **[INSERT LINK]**, we will only focus on significant results in the manuscript.

# Results

## Manipulation Check

Compared to truth, lies were rated with less confidence ($\beta=-1.09,~95\%~CI~[-0.94, -1.25],~pd = 100\%$). Moreover, lies told in the polygraph condition were rated with less confidence ($\delta=-0.24,~95\%~CI~[-0.10, -0.39],~pd > 99\%$). The RT did not differ between truth and lies, but was significantly slower in the polygraph condition ($\beta=0.14,~95\%~CI~[0.03, 0.25],~pd > 99\%$) for both conditions. The heart rate was significantly more elevated during lies as compared to truth ($\beta=1.31,~95\%~CI~[2.14, 0.50],~pd > 99.9\%$), and during interrogation as compared to the polygraph condition ($\beta=4.99 ,~95\%~CI~[5.82, 4.19],~pd = 100\%$).

The indirect phrasing of the question only had a significant effect on RT ($\beta=0.34,~95\%~CI~[0.23, 0.44],~pd = 100\%$), leading to slower answers, regardless of whether they were lies or truths.

## Feature Reduction

The 3 YONI-task dimensions and the 2 BES traits were combined into a unique factor, labelled *Theory of Mind* (explaining 35.76% of variance). It was loaded by the cognitive (.89), affective (.77), physical (.45) YONI dimension, and the affective (.41) and cognitive (.17) traits of the BES.

The 8 MAIA dimensions and the 3 HCT components were reduced to 4 factors (explaining 65.17% of variance). The first factor, labelled *Interoception - Meta* (23.59%), was loaded primarily by Attention Regulation (.97), Self-regulation (.63), Emotional awareness (.60), and noticing (.49) dimensions of the MAIA and the HCT confidence score (.40). The second factor, labelled *Interoception - Listening* (18.54%), was primarily loaded by the body listening (.92) and trusting (.53) MAIA dimensions, and the awareness (-.60) and confidence (.46) HCT scores. The third factor, labelled *Interoception - Focus* (12.07%), was primarily loaded by MAIA not-distracting (.87), emotional awareness (-.40) and HCT accuracy (.33). The fourth factor, labelled *Interoception - Regulation* (10.97%), was primarily loaded by MAIA not-worrying (.71), HCT accuracy (.61) and MAIA trusting (.40). However, due to the interpretation difficulty, we will refer to these dimensions with their main correlates in **Figure 1**.

## Theory of Mind

The composite *ToM* score was significantly associated with less confident ($\beta=-0.19,~95\%~CI~[-0.36, -0.02],~pd = 98.47\%$) and slower lies ($\beta=0.42,~95\%~CI~[0.01, 0.83],~pd = 97.67%\%$), specifically in the polygraph condition. No significant effect was found heart rate, and no correlation with the deception scale traits.

## Interoception

The *Meta* interoception score was significantly associated with an increased confidence in lies, specifically in the polygraph condition ($\beta=0.20,~95\%~CI~[0.03, 0.35],~pd = 98.98\%$). It was also associated with faster answers for both lies ($\beta=-0.54,~95\%~CI~[-0.93, -0.15],~pd = 99.67\%$) and truths ($\beta=-0.29,~95\%~CI~[-0.63, 0.03],~pd = 96.10%\%$), specifically in the polygraph condition. No significant association was found with heart rate.

The *Listening* interoception score was significantly associated with an increased confidence in lies, in the polygraph ($\beta=0.43,~95\%~CI~[0.27, 0.59],~pd = 100\%$) and interrogation condition ($\beta=0.16,~95\%~CI~[0.01, 0.32],~pd = 98.04\%$). It was also associated with faster answers, particularly for lies ($\beta=-0.42,~95\%~CI~[-0.82, -0.03],~pd = 98.19\%$) and truths ($\beta=-0.36,~95\%~CI~[-0.76, 0.03],~pd = 96.49\%$) in the polygraph condition. No significant association was found with heart rate. This score also correlated with the deception *Contextuality* trait ($r = 0.50,~95\%~CI~[0.04, 0.64],~BF_{10} = 3.48\%$).

The *Focus* interoception score was significantly associated with an increased confidence in truthful responses in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$) and interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76%\%$). No significant association was found with RT or heart rate, but the score correlated with the deception *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$).

The *Regulation* interoception score was significantly associated with an increased confidence in lies in the polygraph ($\beta=0.32,~95\%~CI~[0.14, 0.51],~pd = 99.99\%$) and the interrogation conditions ($\beta=0.18,~95\%~CI~[0.00, 0.36],~pd = 97.42\%$), and with a decreased confidence in truth only in the polygraph condition ($\beta=-0.1,~95\%~CI~[-0.36, 0.01],~pd = 97.16\%$). No significant association was found with RT or heart rate.

# Discussion

This study aimed to examine the relationship between Theory of Mind and interoception on lie confidence, reaction time and physiological arousal during deception. This was achieved through a directed lying task in which participants underwent two conditions of false feedback where they were intended to rely on either interoceptive or ToM abilities. Our most notable result is the link between interoception and lying ability,

That the relationship was found largely in the polygraph condition indicates that our manipulation was successful, and further indicates a potential metacognitive element to this link.

<!-- Confidence-->

See the relationship in confidence ratings - subjective nature/variables and noise/reliability

Regarding interoception and confidence, all factors show a significant effect in the polygraph condition, however, the individual interoceptive factors showed unique associations.

Meta Interoception associated with increased confidence in lies in polygraph

<!-- Reaction Time-->

Meta associated with faster answers for lies and truths in polygraph

Listening interoception faster lies and truths in poly

Focus and regulation no RT

<!-- Heart Rate-->

Since we expected heart rate to be associated with theory of mind abilities and condition, our finding of no such relationship was unexpected.

Manipulation checks show elevated cardiac response in lie conditions, so indicative of TOM or Interoception

A potential explanation for this is that the presence of another person, whom they believe is observing them is understood to increase an individual's interoceptive accuracy [@hazem2017know; @isomura2020direct], which may in turn, cause the participant to attempt to regulate their cardiac response.

Greater ToM abilities negatively correlated with lie confidence, and saw an increase in truth confidence, but only in the polygraph condition. In the Yoni Task, this effect is driven by the cognitive and physical domains. BES saw the effect driven by both the cognitive and affective domain for lie confidence, meanwhile, truth confidence is only driven by the affective domain.

<!-- (mostly irrelevant) Scraps -->

Since research has shown deception is more likely when individuals judge a lower risk of confrontation or being caught [@sip2012if; @sip2013pinocchio], these results may offer support to the literature that implicates IA with immoral behaviour. Thus our research may be in support of the findings from @vabba2022interoceptive, where IA was found to be a significant moderator in participant's propensity toward deception and high egoist lies. Similar findings have also linked increased bodily awareness was linked to a greater likelihood of engaging in immoral behavior such as cheating [@williams2016valjean], and risk-taking behaviours [@ditto2006visceral; @lenggenhager2013listening]. However, more research is required to examine this potential link.

Focus interoception associated with increase confidence in truthful response in both conditions

Regulation Interoception associated with increased confidence in lies in both conditions and decreased confidence in truth in the polygraph only

those with greater interoceptive ability would be better at perceiving and regulating physiological arousal [@megias2019emotionally], we expected to see this result in the polygraph condition which emphasizes interoceptive abilities.

## Limitations and Future Research

future research see if interoceptive better at fabricating false emotions

-   limitation that the lying task is very subjective, and the quality of the lie was not measured

# Funding

# Author Contributions

# Conflict of Interest Statement

# Acknowledgements

\newpage

# References

```{r create_r-references}
r_refs(file = "references.bib")
```

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs}
:::

```{=tex}
\endgroup
```
